\section{Experience}
\textsc{Staff Engineer\hfill Feb 2024 - Present\\}
\textsc{Google \hfill Remote, NJ\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
  \item Led the Google Ad Manager response to Privacy Sandbox for video, publishing
        \href{https://github.com/google/ads-privacy/tree/master/proposals/protected-audience-video}{Protected Audience API for Video}.
		Impact of revenue loss mitigation estimated to be 9 figures.
  \item Created a 'Zero-Latency' roadmap for video advertising through full-stack technical design and implementation. Initial results have a realized impact of
  		70\% on key Connected-TV segments.
      % using predictive ad downloading to enable offline video playback and just-in-time ad decisioning, via interstitials for rev max
  \item Created and led a task force to improve fraud detection while improving inventory access, across 4 product areas.
\end{itemize}
        

\textsc{Fan of Isaac Asimov\hfill Formative Years - Present\\}
\textsc{AI Hobby \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}

    \item (aside) From a young age, I have had a deep fascination with SciFi literature and coding. I have fond memories of staying up late after school to read PDFs about modeling neurons in C++.

    \item A few years later, I was running bots to automate online mmorpg games. To evade bot-hunters I downloaded and annotated hundreds of Captchas to train a home-brew python OCR.
    % \item Wrote tools for online games, including real-time analytics comparing 800+ registered users - peaking at 1k QPS, running on a bargain linode server.

    \item My current project is a generative agent-based simulation (inspired by Concordia) of a language learning study-group. It is interactive through a diy Discord chatbot.
\end{itemize}


\textsc{Tech Lead/Manager\hfill Mar 2021 - Feb 2024\\}
\textsc{Google \hfill Remote, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
  \item Drove development of 16 distinct binaries enabling advertising in video players across Web, App and TV.
  \item Scaled product offering by emphasizing developer scalability and investments in tooling + automation.
  \item Responsible for xx trillion ad requests/year and 3x growth in impressions in my tenure.
  \item Developed the next generation of leads, including 4 promotions, while growing the team from 4 to 9 members.
\end{itemize}

  
\textsc{Tech Lead\hfill Feb 2018 - Mar 2021\\}
\textsc{Google \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
  \item Championed and implemented a solution to bring Google-signed-in personalization to video advertising on Android.

  \item This new module is running on 1B+ devices, enabling low-latency cross-device advertising and unlocked a critical business partnership.
 
  \item Due to its performance and handling of user-privacy it has been generalized and expanded to solve for gBid (2023), AdMob (2023), GoogleTV (2024) and Waze (2025).

  \item Oversaw implementation of GDPR, CCPA and COPPA compliance for digital video advertising, impacting 2B+ impressions/day.

%  \item Design and lead global strategy for Ads Transparency for Connected TV devices including Android TV, Apple TV, Roku, FireTV and Chromecast.

%  \item Tech Lead for Android Video Advertising SDK. Handles 400m+ impressions/day and earns 3x revenue per impression as display ads.
        %Decreased error rates by 30\%+ through code-quality and simplification.

  %\item Tech Lead for Cross Platform User Privacy and Regulations - handling 400m+ impressions daily. 

  %\item Designed and productionized a smart preloading feature which showed a 48\% improvement in time to first-frame for video playback.

  %\item Built symbiotic relationships with diverse stakeholders like Android OS, ExoPlayer, AdMob, Ad Spam and Play Store. Leads to better code-reuse and cross-product test strategies.

  %\item Often performing design reviews, code reviews of Java/JS/Python, business modeling, work estimation and road mapping.

  %\item Led cross-vertical initiative with Chromium team to launch Stale-While-Revalidate header caching which improved global median page load time by 2.5\%.
\end{itemize}

\textsc{Engineering Manager\hfill April 2016 - Jan 2018\\}
\textsc{JW Player \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Interviewed, hired and built out the Data organization from 8 members to 30, as part of four independent teams.
	\item Successfully helped principal and senior engineers with career planning and coaching, through humbleness and asking questions.
	%\item Worked closely with Product Management to plan quarterly and annual roadmaps for each team.
	\item Drove data architecture decisions when scaling data systems, from 15k req/sec to 60k req/sec.
	%\item Emphasized automation and iteration to increase release velocity from 2/month to 3/week.
	\item Perform technical comparisons and break-even analysis of technology stacks, then negotiated package pricing with cloud providers including AWS, Snowflake and ModeAnalytics.
	% \item Revamped processes for Database Changes and Incident Response to 70 engineers across 8 teams; decreasing service outages from 0.15\% to 0.01\% weekly.
	% \item Created onboarding program for new engineers which has helped 20+ new hires hit the ground running.
\end{itemize}


\textsc{Senior Software Engineer\hfill May 2014 - April 2016\\}
\textsc{JW Player \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
  \item Redesigned the Javascript message bus for higher performance, shaving 20\% off startup time, across 1 billion plays per month.
  \item Lead Engineer on implementing VPAID2 specification from the IAB, HLS standard from Apple, and Chromecast from Google.
  \item Prototyped and built a full-stack testing framework combining automated and manual tests. Regression testing decreased from 4 weeks to 1.5 weeks.
\end{itemize}


\textsc{Software Engineer\hfill June 2012 - April 2014\\}
\textsc{FactSet Research Systems \hfill New York, NY\\}
\begin{itemize}
  \setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Technical Lead on several web applications, setting the record for fastest rendering time among hundreds.
	\item Created a tool \textit{p4-compare}, which let developers compare the cyclomatic complexity of their code
	changes against the baseline before committing it.
	\item Built out a toolkit for rapidly prototyping new reports, allowing teams in New York, Norwalk and London to search and share code as reusable modules.
	\item Learned to maintain, extend, and love legacy codebases. Or at least love refactoring them.
\end{itemize}





\textsc{Research Fellowship with Xerox\hfill June 2011 - May 2012\\}
\textsc{University of Rochester HCI Lab \hfill Rochester, NY\\}
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\leftmargin}{-5mm}
      \item Researched crowd-sourced real-time audio transcription for hearing-impaired internet users.
      \item Developed a management application for Amazon Mechanical Turk which allowed faster iteration on experiments.
      % \item Participated in project planning, design, and development of services for gathering and retaining Amazon Mechanical Turk workers.
      \item Awarded Xerox Fellowship for contributions to real-time processing of crowd inputs.
\end{itemize}
