\documentclass[oneside, final]{scrartcl}
 
% For line-spacing of header
%  http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/soul/soul.pdf
\usepackage{soul}

% For fancy title
\usepackage{titlesec}

% For comments
\usepackage{verbatim}

% For the icons
\usepackage{marvosym}

% For greying of skills
\usepackage{tabularx,colortbl}

\usepackage[
    margin=2cm
]{geometry}

\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{1.75in}
\addtolength{\textwidth}{.5in}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}
\definecolor{light-gray}{gray}{0.9}
\newcommand{\lang}[1]{\colorbox{light-gray}{\texttt{#1}}}

 
\begin{document}
\begin{center}
 
\textsc{\LARGE{\so{Donato E. Borrello}}}\\
\so{4 Park Avenue \#9B, New York, NY 10016}\\
\so{ {\Large\Letter} venar303@gmail.com \ {\Large\Telefon} (917) 280-0069}

\section{Education}
Bachelor of Science, Computer Science\hfill May 2012\\
University of Rochester\hfill Rochester, NY\\

\section{Development Experience}
\textsc{JW Player \hfill New York, NY\\}
\textsc{Lead Engineer \hfill April 2016 - Present\\}
\textsc{Senior Software Engineer \hfill May 2014 - April 2016\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Technical Lead on projects for the embedded player - scale is currently 17 billion plays per month.
	\item Redesigned the internal message bus for higher performance, shaving 20\% off startup time.
	\item Lead Enginner on implementing VPAID2 specification from the IAB, HLS standard from Apple, and Chromecast from Google.
	\item Prototyped and built a full-stack testing framework, to combine automated and manual tests. Regression testing time went from 4 weeks to 1.5 weeks.
	\item Created onboarding program for new engineers which has helped 20+ new hires hit the ground running.
	\item Revamped Incident Response process which decreased service outages from 0.15\% to 0.01\%
\end{itemize}

\textsc{FactSet Research Systems \hfill June 2012 - April 2014\\}
\textsc{Software Engineer\hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Full stack development, at individual report level and at infrastructure level.
	\item Performed as Technical Lead on the production of Portfolio Manager Snapshot. This analytics report had the fastest rendering time among the hundreds in the CoMA division of FactSet.
	\item Created a tool \textit{p4-compare}, which let developers compare the cyclomatic complexity of their change against what is in master.
%	\item Learned to maintain, extend, and love legacy codebases. Or at least love refactoring them. Never learned to love VMS.
%	\item Mentored two new engineers, and is very active in code reviews.
	\item Trusted to work across departments creating a new Backbone toolkit for rapidly prototyping new reports. It is currently improving productivity for teams in New York, Norwalk and London.
\end{itemize}

\textsc{University of Rochester HCI Lab \hfill June 2011 - May 2012\\}
\textsc{Research Fellowship with Xerox\hfill Rochester, NY\\}
\begin{itemize}
 \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
 \setlength{\leftmargin}{-5mm}
  \item Our project provided economically viable real-time audio transcription for hearing-impaired internet users. Personal contributions were recognized through a Xerox Fellowship.
  \item Developed PHP-API for Amazon Mechanical Turk which allowed easier integration of external data-sources and enhanced real-time processing capabilities.
  \item Participated in project planning, design, and development of services for gathering and retaining Amazon Mechanical Turk workers.
\end{itemize}



\textsc{Freelance \hfill  Childhood - Present\\}
\textsc{Fullstack Game Programmer\hfill Rochester, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Created a new interface to an online game, Kings of Chaos, to enhance and improve fundamental gameplay.
	\item Wrote server software to provide dynamic analytics comparing 800+ registered users over 5 years. At peak, the system logged 1,472,038 user-events in one month January, 2009.
	\item Wrote a bot to simulate human interaction, automating every aspect of gameplay. Required header-spoofing, captcha cracking, and basic NLP. (Don't tell the admins!)
\end{itemize}

% End first page
\clearpage


 \begin{comment}

\textsc{Intellisites \hfill Summer 2009, 2010\\}
\textsc{Web Developer\hfill Albany, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Performed security audits on legacy websites for OWASP Top-10 vulnerabilities including SQL injection, Cross-site Scripting and configuration problems.
	\item Wrote file management application with granular user access control and permissions. Application allowed productivity increases in client office.
\end{itemize}

 \end{comment}


\section{Conferences}
\begin{flushleft}
\textbf{The Nitty Gritty of Adaptive Video Transmuxing \hfill EmpireJS, 2016\\}
A 30 minute presentation on strategies for efficiently transmuxing video for improving the
time to first frame. The core principal is switching from batch computation to streaming.
I discuss why Communicating Sequential Processes (CSP) works as a strong alternative to streams with back pressure.
\end{flushleft}

\section{Publications}
\begin{flushleft}
\textbf{Real time Captioning by Non-Experts\\}
Nominated for best paper in the the 25th Annual UIST Conference 2012: 23-34\\

\vspace{10pt}

\textbf{Online Sequence Alignment for Real-Time Audio Transcription by Non-Experts \\}
Published by the 26th Annual AAAI Conference 2012\\
\end{flushleft}


\section{Other Contributions}
\begin{itemize}
    \item CIO of Beach Recovery Foundation, non-profit organization working to reverse human effect on beach erosion
    \item CTO of Simplify Reality, distills current events into 400 word summaries for millennials
    \item Consultant for AI-Coin, a bitcoin variant which sacrifices decentralization for sub-second transactions
    \item Maintainer of Google's Karma repository
    \item Code contributor to Google's Shaka Video player
    \item Code contributor to Blender, the open-source 3D modeling engine
    \item Art contributor to Planeshift, the first open-source mmorpg
    \item Security research for Kings Of Chaos, helping fix nginx configuration to mitigate a slowloris attack
    \item Member of think-tank for MiMedia, a Brooklyn based startup for cloud storage of media
\end{itemize}


\section{Lists}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item \textbf{Job Experience:}  \lang{Javascript}, \lang{C++}, \lang{Node}, \lang{TypeScript}, \lang{Mongodb}, and \lang{git}
	\item \textbf{Fun Stuff:}  \lang{Java}, \lang{Python}, \lang{Haskell}, \lang{Starcraft}, \lang{Database Design}, \lang{CUDA}, \lang{Ruby} \\
	\item \textbf{Favorite Places:}
        \lang{New York, New York},
        \lang{Puglia},
        \lang{Turks'n Caicos},
        \lang{Tamarindo},
        \lang{Buenos Aires}
        \\
\end{itemize}


\end{center}
\end{document}