\documentclass[oneside, final]{scrartcl}
 \pdfmapfile{fontawesome.map}
% For line-spacing of header
%  http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/soul/soul.pdf
\usepackage{soul}

% For fancy title
\usepackage{titlesec}

% For comments
\usepackage{verbatim}

% For the icons
\usepackage{marvosym}
%\usepackage{fontspec}
\usepackage{fontawesome}

% For greying of skills
\usepackage{tabularx,colortbl}

\usepackage[
    margin=2cm
]{geometry}

\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{1.75in}
\addtolength{\textwidth}{.5in}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}
\definecolor{light-gray}{gray}{0.9}
\newcommand{\lang}[1]{\colorbox{light-gray}{\texttt{#1}}}

 
\begin{document}
\begin{center}
 
\textsc{\LARGE{\so{Donato E. Borrello}}}\\
\so{4 Park Avenue \#9B, New York, NY 10016}\\
{\Large\Letter} venar303@gmail.com \ {\Large\Telefon} (917) 280-0069 \ \faGithub \ github.com/donato



\section{Education}
Bachelor of Science, Computer Science\hfill May 2012\\
University of Rochester\hfill Rochester, NY\\


\section{Experience}
\textsc{Lead Engineer\hfill April 2016 - Present\\}
\textsc{JW Player \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Hire and lead Analytics and Business Intelligence teams to self-sufficiency, guiding them to timely completion of projects.
	\item Emphasized automation and iteration to increase release velocity from 2/month to 3/week.
	\item Drive data architecture decisions when scaling data systems, from 15k req/sec to 60k req/sec.
	\item Revamped processes for Database Changes and Incident Response to 70 engineers across 8 teams; decreasing service outages from 0.15\% to 0.01\% weekly.
	\item Perform technical comparisons and break-even analysis of technology stacks, then negotiated package pricing with cloud providers including AWS, Snowflake and ModeAnalytics.
	% \item Rolled out Database Change process to 50 engineers across 6 teams.
	% \item Created onboarding program for new engineers which has helped 20+ new hires hit the ground running.
\end{itemize}

\textsc{Senior Software Engineer\hfill May 2014 - April 2016\\}
\textsc{JW Player \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
        \item Redesigned the Javascript message bus for higher performance, shaving 20\% off startup time, across 1 billion plays per month.
        \item Lead Engineer on implementing VPAID2 specification from the IAB, HLS standard from Apple, and Chromecast from Google.
        \item Prototyped and built a full-stack testing framework combining automated and manual tests. Regression testing decreased from 4 weeks to 1.5 weeks.
\end{itemize}

\textsc{Software Engineer\hfill June 2012 - April 2014\\}
\textsc{FactSet Research Systems \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Technical Lead on several web applications, setting the record for fastest rendering time among hundreds.
	\item Created a tool \textit{p4-compare}, which let developers compare the cyclomatic complexity of their code
	changes against master before checking it in.
	\item Learned to maintain, extend, and love legacy codebases. Or at least love refactoring them.
\end{itemize}

\textsc{Full Stack Game Developer\hfill June 2008 - April 2012\\}
\textsc{Freelance\hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Created a new interface to a text-based MMORPG, to enhance and improve fundamental gameplay.
    \item Provided real-time analytics comparing 800+ registered users - at peak popularity 50k writes per day.
    \item Wrote bots to simulate human interaction, automating every aspect of gameplay. Required header-
            spoofing, captcha cracking, and basic NLP. (Don’t tell the admins!)
\end{itemize}


\begin{comment}
    \textsc{Research Fellowship with Xerox\hfill Rochester, NY\\}
    \textsc{University of Rochester HCI Lab \hfill June 2011 - May 2012\\}
    \textsc{Research Fellowship with Xerox\hfill Rochester, NY\\}
    \begin{itemize}
      % \vspace{-8pt}
      \setlength{\itemsep}{1pt}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\leftmargin}{-5mm}
          \item Researched crowd-sourced real-time audio transcription for hearing-impaired internet users.
          \item Developed a management applicaton for Amazon Mechanical Turk which allowed faster iteration on experiments.
          \item Awarded Xerox Fellowship for contributions to real-time processing of crowd inputs.
          \item Participated in project planning, design, and development of services for gathering and retaining Amazon Mechanical Turk workers.
    \end{itemize}
\end{comment}


\section{Community}
\begin{flushleft}

    \textbf{The Nitty Gritty of Adaptive Video Transmuxing} \hfill May  2016\\
    A technical talk at the EmpireJS Conference on efficiently transmuxing video in javascript for improving time to first frame, with over 400 attendees.

    \vspace{10pt}

    \textbf{Real time Captioning by Non-Experts} \hfill October  2012\\
    A white-paper on crowd-sourcing, nominated for best paper in the the 25th Annual UIST Conference.

    %\vspace{10pt}

    %\textbf{Online Sequence Alignment for Real-Time Audio Transcription by Non-Experts \hfill July, 2012\\}
    %A white-paper on aligning crowd-sourced inputs in time, published by the 26th Annual AAAI Conference.

\end{flushleft}


\begin{comment}

    \section{Lists}
    \begin{itemize}
        \setlength{\itemsep}{1pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \setlength{\leftmargin}{-5mm}
        \item \textbf{Job Experience:}
            \lang{C++},
            \lang{Javascript},
            \lang{Python},
            \lang{Java},
            \lang{Node}, and
            \lang{SQL} \\
        \item \textbf{Fun Stuff:}
            \lang{Haskell},
            \lang{Starcraft},
            \lang{TypeScript},
            \lang{Gardening}, and
            \lang{p5.js} \\
        \item \textbf{Favorite Places:}
            \lang{New York},
            \lang{Puglia},
            \lang{Turks'n Caicos},
            \lang{Tamarindo}, and
            \lang{Buenos Aires}
    \end{itemize}
\end{comment}

\end{center}
\end{document}