\documentclass[oneside, final]{scrartcl}
 
% For line-spacing of header
%  http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/soul/soul.pdf
\usepackage{soul}

% For fancy title
\usepackage{titlesec}

% For comments
\usepackage{verbatim}

% For the icons
\usepackage{marvosym}

% For greying of skills
\usepackage{tabularx,colortbl}

\usepackage[
    margin=2cm
]{geometry}

\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{1.75in}
\addtolength{\textwidth}{.5in}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}
\definecolor{light-gray}{gray}{0.9}
\newcommand{\lang}[1]{\colorbox{light-gray}{\texttt{#1}}}

 
\begin{document}
\begin{center}
 
\textsc{\LARGE{\so{Donato E. Borrello}}}\\
\so{4 Park Avenue \#9B, New York, NY 10016}\\
\so{ {\Large\Letter} venar303@gmail.com \ {\Large\Telefon} (917) 280-0069}

\section{Summary}
\begin{flushleft}
Motivated and enthusiastic technology leader with 15 years of experience writing semicolons, leading teams and delivering products. Has repeatedly been able to dive-deep on technical problems and emerge as a thought-leader in various fields. Recognized for his ability to gather information and provide a clear vision for achieving both short and long-term goals. Able to translate needs from business to the technical side and back. Proven track-record for hiring a talented, complementary, and highly effective team.
\end{flushleft}


\section{Education}
Bachelor of Science, Computer Science\hfill May 2012\\
University of Rochester\hfill Rochester, NY\\

\section{Experience}
\textsc{JW Player \hfill April 2016 - Present\\}
\textsc{Lead Engineer\hfill New York, NY\\}
\begin{itemize}
    \vspace{-4pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Hired and led a team of 8 to be self-sufficient, guiding them to timely completion of projects.
	\item Iteratively delivered products, which doubled customer engagement twice in 6 months.
	\item Drove data architecture decisions when scaling systems to handle over 60k events/sec.
	\item Centralized information related to systems architecture and created the de-facto blueprint used by all members of our organization.
	\item Pushed a values-driven culture and empowered IC's to make trade-offs independently when appropriate. 
	%\item Drive data architecture decisions when scaling systems, such as Storm from 25k req/sec to 50k req/sec.
	\item Performed technical comparisons and break-even analysis of technology stacks, then negotiated package pricing with cloud providers including AWS, Snowflake and ModeAnalytics.
	\item Revamped processes for Database Change Management and Incident Response to 50 engineers across 6 teams; decreasing service outages from 0.15\% to 0.01\% weekly.
	% \item Created onboarding program for new engineers which has helped 20+ new hires hit the ground running.
\end{itemize}

\textsc{JW Player \hfill May 2014 - April 2016\\}
\textsc{Senior Software Engineer\hfill New York, NY\\}
\begin{itemize}
    \vspace{-4pt}
	\setlength{\itemsep}{1pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	% \item Technical Lead on projects for the embedded player - scale is currently 17 billion plays per month.
	\item Lead Engineer on implementing VPAID2 specification from IAB, which services over 250M ads/month.
	\item Lead Engineer on implementing HLS standard from Apple, which services over 6Bn video streams/month.
	\item Redesigned the javascript message bus for higher performance, shaving 20\% off startup time.
	\item Prototyped and built a full-stack testing framework \textit{Squash} to combine automated and manual tests.
	\item Through iterative development, \textit{Squash} decreased regression testing from 4 weeks to 1 week, to 3 days.
\end{itemize}

\textsc{FactSet Research Systems \hfill June 2012 - April 2014\\}
\textsc{Software Engineer\hfill New York, NY\\}
\begin{itemize}
    \vspace{-4pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Performed as Technical Lead on a full stack analytics reporting application, which had the fastest rendering time among hundreds in the CoMA division of FactSet.
	\item Learned to maintain, extend, and love legacy codebases. Or at least love refactoring them. Never learned to love VMS.
	\item Created a tool \textit{p4-compare}, which let developers compare the cyclomatic complexity of their change against what is in master.
%	\item Mentored two new engineers, and is very active in code reviews.
	\item Worked across departments creating a new Backbone toolkit for rapidly prototyping new reports. It is currently improving productivity for teams in New York, Norwalk and London.
\end{itemize}




% End first page
\clearpage



\textsc{Rochester Human-Computer-Interaction Group \hfill June 2011 - May 2012\\}
\textsc{Research Fellowship with Xerox\hfill Rochester, NY\\}
\begin{itemize}
  \vspace{-4pt}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\leftmargin}{-5mm}
  \item Researched methods to provide economically viable real-time audio transcription for hearing-impaired internet users.
  \item Developed PHP-API for Amazon Mechanical Turk which allowed easier integration of external data-sources and enhanced real-time processing capabilities.
  \item Participated in project planning, design, and development of services for gathering and retaining Amazon Mechanical Turk workers.
 % \item Awarded Xerox Fellowship for my personal contributions
\end{itemize}



\textsc{Freelance \hfill  Childhood - Present\\}
\textsc{Full Stack Game Developer\hfill Rochester, NY\\}
\begin{itemize}
    \vspace{-4pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Created a new interface to an online game, Kings of Chaos, to enhance and improve fundamental gameplay.
	\item Provided real-time analytics comparing 800+ registered users over 13 years.
	 %At peak, the system logged 1,472,038 user-events in one month January, 2009.
	\item Wrote bots to simulate human interaction, automating every aspect of gameplay. Required header-spoofing, captcha cracking, and basic NLP. (Don't tell the admins!)
\end{itemize}


\section{Conferences}
\begin{flushleft}
\textbf{The Nitty Gritty of Adaptive Video Transmuxing \hfill EmpireJS, 2016\\}
A 30 minute presentation on strategies for efficiently transmuxing video for improving the
time to first frame. The core principal is switching from batch computation to streaming.
I discuss why Communicating Sequential Processes (CSP) works as a strong alternative to streams with back pressure.
\end{flushleft}

\section{Publications}
\begin{flushleft}


\section{Other Contributions}
\begin{itemize}
   \begin{comment}
        \item CIO of Beach Recovery Foundation, non-profit working to reverse human effect on beach erosion
        \item CTO of Simplify Reality, distills current events into 400 word summaries for millennials
    \end{comment}
    \item Founder of Election Reform New York - a group pushing for Instant Run Off elections in NY
    \item Maintainer of Google's Karma repository, a javascript test runner
    \item Code contributor to Google's Shaka repository, a DASH video player
    \item Code contributor to Blender, an open-source 3D modeling engine
    \item Security research for KingsOfChaos.com, a text-based mmo
    \item Art contributor to Planeshift.it, an open-source 3D mmorpg
    \item Consultant for AI-Coin, a bitcoin variant which sacrifices decentralization for sub-second transactions
    \item Member of think-tank for MiMedia, a Brooklyn based startup for cloud storage of media
\end{itemize}



\section{Lists}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item \textbf{Job Experience:}
        \lang{C++},
        \lang{Javascript},
        \lang{Python},
        \lang{Java},
        \lang{Node}, and
        \lang{SQL} \\
	%\item \textbf{DB's in Prod:} \lang{Redis}, \lang{Mongo}, \lang{PostgreSQL}, \lang{MySQL} \\
	\item \textbf{Fun Stuff:}
        \lang{Haskell},
        \lang{Starcraft},
        \lang{TypeScript},
        \lang{Gardening}, and
        \lang{p5.js} \\
	\item \textbf{Not lovin' it:}
        \lang{tabs},
        \lang{Flask},
        \lang{lag},
        \lang{Angular},
        \lang{Pager Duty} \\
	\item \textbf{Favorite Places:}
        \lang{New York},
        \lang{Puglia},
        \lang{Turks'n Caicos},
        \lang{Tamarindo}, and
        \lang{Buenos Aires}
\end{itemize}



\end{center}
\end{document}