\documentclass[oneside, final]{scrartcl}
 
% For line-spacing of header
%  http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/soul/soul.pdf
\usepackage{soul}

% For fancy title
\usepackage{titlesec}

% For comments
\usepackage{verbatim}

% For the icons
\usepackage{marvosym}

% For greying of skills
\usepackage{tabularx,colortbl}

\usepackage[
    margin=2cm
]{geometry}

\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{1.75in}
\addtolength{\textwidth}{.5in}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}
\definecolor{light-gray}{gray}{0.9}
\newcommand{\lang}[1]{\colorbox{light-gray}{\texttt{#1}}}

 
\begin{document}
\begin{center}
 
\textsc{\LARGE{\so{Donato E. Borrello}}}\\
\so{4 Park Avenue \#9B, New York, NY 10016}\\
\so{ {\Large\Letter} venar303@gmail.com \ {\Large\Telefon} (917) 280-0069}

\section{Education}
Bachelor of Science, Computer Science\hfill May 2012\\
University of Rochester\hfill Rochester, NY\\

\section{Experience}
\textsc{JW Player \hfill New York, NY\\}
\textsc{Lead Engineer\hfill April 2016 - Present\\}
\begin{itemize}
    \vspace{-8pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Hire and lead a team of 8 to be self-sufficient, guiding them to timely completion of projects.
	\item Drive data architecture decisions when scaling systems, such as Storm from 25k req/sec to 50k req/sec.
	\item Perform technical comparisons and break-even analysis of technology stacks, then negotiated package pricing with cloud providers including AWS.
	\item Revamped processes for Database Changes and Incident Response to 50 engineers across 6 teams; decreasing service outages from 0.15\% to 0.01\% weekly.
	% \item Rolled out Database Change process to 50 engineers across 6 teams.
	% \item Created onboarding program for new engineers which has helped 20+ new hires hit the ground running.
\end{itemize}

\textsc{JW Player \hfill New York, NY\\}
\textsc{Senior Software Engineer\hfill May 2014 - April 2016\\}
\begin{itemize}
    \vspace{-8pt}
	\setlength{\itemsep}{1pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	% \item Technical Lead on projects for the embedded player - scale is currently 17 billion plays per month.
	\item Redesigned the Javascript message bus for higher performance, shaving 20\% off startup time.
	\item Lead Engineer on implementing VPAID2 specification from the IAB, HLS standard from Apple, and Chromecast from Google.
	\item Prototyped and built a full-stack testing framework combining automated and manual tests. Regression testing decreased from 4 weeks to 1.5 weeks.
\end{itemize}

\textsc{FactSet Research Systems \hfill June 2012 - April 2014\\}
\textsc{Software Engineer\hfill New York, NY\\}
\begin{itemize}
    \vspace{-8pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Performed as Technical Lead on the production of Portfolio Manager Snapshot. This analytics report had the fastest rendering time among the hundreds in the CoMA division of FactSet.
	\item Created a tool \textit{p4-compare}, which let developers compare the cyclomatic complexity of their change against what is in master.
\end{itemize}


\textsc{University of Rochester HCI Lab \hfill June 2011 - May 2012\\}
\textsc{Research Fellowship with Xerox\hfill Rochester, NY\\}
\begin{itemize}
  \vspace{-8pt}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\leftmargin}{-5mm}
  \item Researched methods to provide economically viable real-time audio transcription for hearing-impaired internet users. 
  \item Developed PHP-API for Amazon Mechanical Turk which allowed easier integration of external data-sources and enhanced real-time processing capabilities.
    \item Awarded Xerox Fellowship for my personal contributions.

%  \item Participated in project planning, design, and development of services for gathering and retaining Amazon Mechanical Turk workers.
\end{itemize}





\section{Conferences}
\begin{flushleft}
\textbf{The Nitty Gritty of Adaptive Video Transmuxing \hfill EmpireJS, 2016\\}
A 30 minute presentation on strategies for efficiently transmuxing video for improving the
time to first frame. The core principal is switching from batch computation to streaming.
I discuss why Communicating Sequential Processes (CSP) works as a strong alternative to streams with back pressure.
\end{flushleft}




\section{Lists}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item \textbf{Job Experience:}  \lang{Javascript}, \lang{Python}, \lang{C++}, \lang{Java}, \lang{Node}, \lang{Storm}, and \lang{git} \\
	%\item \textbf{DB's in Prod:} \lang{Redis}, \lang{Mongo}, \lang{PostgreSQL}, \lang{MySQL} \\
	\item \textbf{Fun Stuff:}  \lang{Haskell}, \lang{Starcraft}, \lang{TypeScript}, \lang{Database Design}, \lang{CUDA} \\
	\item \textbf{Favorite Places:}
        \lang{New York, New York},
        \lang{Puglia},
        \lang{Turks'n Caicos},
        \lang{Tamarindo},
        \lang{Buenos Aires}
\end{itemize}


\end{center}
\end{document}