\documentclass[oneside, final]{scrartcl}
\pdfmapfile{fontawesome.map}

% For line-spacing of header
%  http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/soul/soul.pdf
\usepackage{soul}

% For fancy title
\usepackage{titlesec}

% For comments
\usepackage{verbatim}

% For the icons
\usepackage{marvosym}
\usepackage{fontawesome}

% For greying of skills
\usepackage{tabularx,colortbl}

% For page margins
\usepackage[ margin=2cm ]{geometry}

\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\topmargin}{-.30in}
\addtolength{\textheight}{1.75in}
\addtolength{\textwidth}{.5in}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}
\definecolor{light-gray}{gray}{0.9}
\newcommand{\lang}[1]{\colorbox{light-gray}{\texttt{#1}}}

\begin{document}
\begin{center}
 
\textsc{\LARGE{\so{Donato E. Borrello}}}\\
\so{351 West 51st St \#2, New York, NY 10019}\\
{\Large\Letter} venar303@gmail.com \ {\Large\Telefon} (917) 280-0069 \ \faGithub \ github.com/donato

\vspace{-5pt}

\section{Experience}


    \textsc{Senior Software Engineer \hfill November 2019 - Present\\}
    \textsc{Software Engineer \hfill February 2018 - October 2019\\}
    \textsc{Google \hfill New York, NY\\}
    \begin{itemize}
    	\setlength{\itemsep}{1pt}
    	\setlength{\parskip}{0pt}
    	\setlength{\parsep}{0pt}
    	\setlength{\leftmargin}{-5mm}
    	\item Designed and lead global strategy for Ads Transparency for Connected TV devices including Android TV, Apple TV, Roku, FireTV and Chromecast.
    	\item Oversaw implementation of GDPR , CCPA and COPPA compliance for digital Video Advertising, responsible for over 100M ad impressions per day.
    	\item Lead Eng for ad personalization on Android devices. In role, identified and drafted a proposal for "Trustless Ad Personalization" which was reviewed and approved 
    	\item Identified, planned and executed major refactor of IMA SDK, allowing core components to be made immutable.
    	\item Adviser to four 8+ engineer teams as part of Googles Tech Immersion program. 
    	%\item Recruited, hired and couched new hires, while performing dozens of interviews and phone-screens.
    \end{itemize}

\textsc{Engineering Manager\hfill April 2016 - Jan 2018\\}
\textsc{JW Player \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Interviewed, hired and built out the Data organization from 8 members to 30, as part of four independent teams.
	\item Successfully helped staff and senior engineers with career planning and couching, through humility and asking questions.
	\item Worked closely with Product Management to plan quarterly and annual roadmaps for each team.
	\item Drove data architecture decisions when scaling data systems, from 15k req/sec to 60k req/sec.
	%\item Emphasized automation and iteration to increase release velocity from 2/month to 3/week.
	\item Perform technical comparisons and break-even analysis of technology stacks, then negotiated package pricing with cloud providers including AWS, Snowflake and ModeAnalytics.
	\item Revamped processes for Database Changes and Incident Response to 70 engineers across 8 teams; decreasing service outages from 0.15\% to 0.01\% weekly.
	% \item Created onboarding program for new engineers which has helped 20+ new hires hit the ground running.
\end{itemize}


\textsc{Senior Software Engineer\hfill May 2014 - April 2016\\}
\textsc{JW Player \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
        \item Redesigned the Javascript message bus for higher performance, shaving 20\% off startup time, across 1 billion plays per month.
        \item Lead Engineer on implementing VPAID2 specification from the IAB, HLS standard from Apple, and Chromecast from Google.
        \item Prototyped and built a full-stack testing framework combining automated and manual tests. Regression testing decreased from 4 weeks to 1.5 weeks.
\end{itemize}


\textsc{Software Engineer\hfill June 2012 - April 2014\\}
\textsc{FactSet Research Systems \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Technical Lead on several web applications, setting the record for fastest rendering time among hundreds.
	\item Created a tool \textit{p4-compare}, which let developers compare the cyclomatic complexity of their code
	changes against the baseline before committing it.
	\item Built out a toolkit for rapidly prototyping new reports, allowing teams in New York, Norwalk and London to search and share code as reusable modules.
	\item Learned to maintain, extend, and love legacy codebases. Or at least love refactoring them.
\end{itemize}


\textsc{Full Stack Game Developer\hfill June 2008 - April 2012\\}
\textsc{Freelance\hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Created a new interface to a text-based MMORPG, to enhance and improve fundamental gameplay.
    \item Provided real-time analytics comparing 800+ registered users - at peak popularity 50k writes per day.
    \item Wrote bots to simulate human interaction, automating every aspect of gameplay. Required header-
            spoofing, captcha cracking, and basic NLP. (Don’t tell the admins!)
\end{itemize}


    \textsc{Research Fellowship with Xerox\hfill Rochester, NY\\}
    \textsc{University of Rochester HCI Lab \hfill June 2011 - May 2012\\}
    \textsc{Research Fellowship with Xerox\hfill Rochester, NY\\}
    \begin{itemize}
      \setlength{\itemsep}{1pt}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\leftmargin}{-5mm}
          \item Researched crowd-sourced real-time audio transcription for hearing-impaired internet users.
          \item Developed a management application for Amazon Mechanical Turk which allowed faster iteration on experiments.
          \item Awarded Xerox Fellowship for contributions to real-time processing of crowd inputs.
          \item Participated in project planning, design, and development of services for gathering and retaining Amazon Mechanical Turk workers.
    \end{itemize}


% End first page
\clearpage

\section{Education}
Bachelor of Science, Computer Science\hfill May 2012\\
University of Rochester\hfill Rochester, NY\\

 \section{Conferences and Publications}
    
\begin{flushleft}

    \textbf{Election Reform New York} \hfill February  2017 - Present\\
    Founder of a non-profit group, partnered with FairVote, to bring Ranked Choice Voting to New York.
    On June 2019, it was passed in NYC for all municipal primaries and special elections!
    \vspace{10pt}    


    \textbf{Volunteer Manager Sanders Campaign} \hfill November  2019 - Present\\
    Volunteer Manager for 2020 campaign 
    \vspace{10pt}    
        
    \textbf{The Nitty Gritty of Adaptive Video Transmuxing} \hfill May  2016\\
    A technical talk at the EmpireJS Conference on efficiently transmuxing video in javascript for improving time to first frame, with over 400 attendees.
    \vspace{10pt}
    
    \textbf{Real time Captioning by Non-Experts} \hfill October  2012\\
    A white-paper on crowd-sourcing as an alternative to professional services for economically viable audio transcription. Nominated for best paper in the the 25th Annual UIST Conference.
    
\end{flushleft}


    \section{Skills}
    \begin{itemize}
        \setlength{\itemsep}{1pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \setlength{\leftmargin}{-5mm}
       
       % \item Management, Leadership, Performance, Scalability, Systems Architecture, A/B Testing, Mentoring
          %\vspace{2pt}

        \item \textbf{Programming Languages:}
            \lang{C++},
            \lang{Javascript},
            \lang{Python},
            \lang{Java},
            \lang{Node}, and
            \lang{SQL} \\
            
        \item \textbf{Data Experience: }
            \lang{Spark},
            \lang{Storm},
            \lang{Kafka},
            \lang{Hadoop/MR},
            \lang{Hive}, and
            \lang{GraphX} \\

       \item \textbf{Interests:}
            \lang{Music},
            \lang{Election Reform},
            \lang{Gardening}, and
            \lang{Data Visualization} \\
            

        \item \textbf{Favorite Places:}
            \lang{New York},
            \lang{Puglia},
            \lang{Turks'n Caicos},
            \lang{Tamarindo}, and
            \lang{Buenos Aires}

    \end{itemize}

\end{center}
\end{document}