\documentclass[oneside, final]{scrartcl}
 
% For line-spacing of header
%  http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/soul/soul.pdf
\usepackage{soul}

% For fancy title
\usepackage{titlesec}

% For comments
\usepackage{verbatim}

% For the icons
\usepackage{marvosym}

% For greying of skills
\usepackage{tabularx,colortbl}

\usepackage[
    margin=2cm
]{geometry}

\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{1.75in}
\addtolength{\textwidth}{.5in}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}
\definecolor{light-gray}{gray}{0.9}
\newcommand{\lang}[1]{\colorbox{light-gray}{\texttt{#1}}}

 
\begin{document}
\begin{center}
 
\textsc{\LARGE{\so{Tyler M. Bowers}}}\\
\so{241 East 86th St, Manhattan, New York}\\
\so{ {\Large\Letter} tylermb24@gmail.com\ {\Large\Telefon} (518) 542-4552}



\section{Objective}
Seeking a position where I can build on my experience in technology oriented sales organization.
The ideal role will leverage my interpersonal skills and have a career progression into direct sales.

\section{Skills}
\item Upbeat attitude, quick learner and great sense of humor.
\item Strong communication skills, with managers and customers alike.
\item Calm in high stress situations and skilled multitasking/prioritizing during ?the rush.?
\item Hard working, motivated and reliable.
\item Known by coworkers as an honest team player.


\section{Experience}

\textsc{NCSPlus Incorporated \hfill - Present \\}
\textsc{Account Executive \hfill New York, NY\\}
\begin{itemize}
    \item Sales prospecting
    \item x
\end{itemize}

\textsc{Yono's Restaurant \hfill ??? \\}
\textsc{Bar Manager \hfill Albany, NY\\}
\begin{itemize}
    \item Curated a wine list of over 1000 wines, including their origin, geography and characteristics.
    \item Creatively found ways to make angry customers happy without hurting the sale or the servers tip.
    \item Responsible for creating new cocktails and building drink lists.
    \item Trained new bartenders and cocktail servers, even those senior to me without seeming condescending.
    \item Attended wine tastings and choosing new wines for our master wine list.
\end{itemize}

\textsc{Gaonnurri Restaurant\hfill January 2014 - January 2015\\}
\textsc{Bar Captain \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
	\item Tracked and managed bar inventory, as well as negotiating purchasing contracts.
    \item Multitasking and prioritizing during "the rush" which was up to 100 customers.
    \item Trained multiple servers and bartenders in service industry.
\end{itemize}

\textsc{Per Lei \hfill July 2012 - December 2013\\}
\textsc{Bartender\hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
    \item Learned to master service expectations for one of the best fine dining restaurants in NYC.
    \item Dealt with picky customers and getting positive reviews from them.
    \item Calmly and professionally handled high stress situations.
	\item Studied and learned rudimentary Italian to create positive interactions with customers.
\end{itemize}


\end{center}
\end{document}