\documentclass[oneside, final]{scrartcl}
 
% For line-spacing of header
%  http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/soul/soul.pdf
\usepackage{soul}

% For fancy title
\usepackage{titlesec}

% For comments
\usepackage{verbatim}

% For the icons
\usepackage{marvosym}

% For greying of skills
\usepackage{tabularx,colortbl}

\usepackage[
    margin=2cm
]{geometry}

\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{1.75in}
\addtolength{\textwidth}{.5in}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}
\definecolor{light-gray}{gray}{0.9}
\newcommand{\lang}[1]{\colorbox{light-gray}{\texttt{#1}}}

 
\begin{document}
\begin{center}
 
\textsc{\LARGE{\so{Tyler M. Bowers}}}\\
\so{241 East 86th St, Manhattan, New York}\\
\so{ {\Large\Letter} tylermb24@gmail.com \ {\Large\Telefon} (518) 542-4552}



\section{Objective}
\begin{flushleft}
I am seeking a role where I can build on my experience in sales, preferably in a technology driven
organization. The ideal role will leverage my interpersonal skills and have an opportunity for career progression.
\end{flushleft}



\section{Experience}

\textsc{NCSPlus Incorporated \hfill August 2016 - Present \\}
\textsc{Account Executive \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
    \item Responsible for maintaining relationships with clients after making a sale ensuring they are satisfied with the service.
    \item Recognizing the client's business needs and showing how our service would benefit them. 
    \item Continuously qualifying prospects to identify sales with the highest likelihood to succeed.
    \item Responsible for generating lead lists, filtering them and cold-calling potential clients.
    \item When on cold calls, experienced with navigating through the  ``gatekeeper'' and identifying the decision maker. 
\end{itemize}


\textsc{Sunshine Wine Distribution Co. \hfill May 2016 - August 2016 \\}
\textsc{Outside Sales Rep \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
    \item Built relationships with local liquor stores to get Sunshine products on their shelves.
    \item Planned and organized satellite bars to boost sales and build brand awareness.
    \item Coordinated with other sellers in the area to maximize coverage within a neighborhood.
\end{itemize}

\textsc{Yono's Restaurant \hfill August 2015 - June 2016 \\}
\textsc{Bar Manager \hfill Albany, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
    \item Curated a wine list of over 1,000 wines including their origin, geography and characteristics.
    \item Creatively found ways to make angry customers happy without hurting the sale or the servers tip.
    \item Responsible for creating new cocktails and building drink lists.
    \item Trained new bartenders and cocktail servers, even those senior to me without seeming condescending.
    \item Attended wine tastings and chose new products for our master wine list.
\end{itemize}

\textsc{Gaonnurri Restaurant\hfill January 2014 - July 2015\\}
\textsc{Bar Captain \hfill New York, NY\\}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
    \item Tracked and managed bar inventory, as well as negotiating purchasing contracts.
    \item Multitasking and prioritizing during ``the rush'' which was up to 100 customers.
    \item Dealt with picky customers and getting positive reviews from them.
    \item Trained multiple servers and bartenders in the service industry.
    \item Built relationships with hundreds of customers over the course of my time there.

\end{itemize}


\begin{comment}
\section{Education}
Guilderland High School\hfill 2004 - 2008\\
High School Diploma\hfill Albany, NY\\
\end{comment}

\section{Skills}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\setlength{\leftmargin}{-5mm}
    \item Upbeat attitude, quick learner and great sense of humor.
    \item Strong communication skills, with managers and customers alike.
    \item Calm in high stress situations and skilled in multitasking and prioritizing.
    \item Hard working, motivated and reliable.
\end{itemize}

\end{center}
\end{document}